I Compensate, therefore I Am \\ (accurate for DNN verification)

### 2024-01-17 Paper/Paper_noProof.tex
typos

The local robustness verification is performed on DNNs trained for the MNIST image dataset as its the only standard DNNs (MLP $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$) benchmarked by \cite{crown} not using robust training, and they are the hardest DNNs to verify, despite their relatively limited size (600 to 1600 neurons in hidden layers). Indeed, today's efficient methods leave at least $14\%$ to $20\%$ of the images neither certified robust nor with an attack to robustness found, making them interesting DNNs to consider where to improve accuracy of efficient techniques. We also test on the larger MLP $6\times 500$, not previously tested in \cite{crown}. MNIST contains grayscale images of size $28 \times 28$ pixels ($752$ input neurons). For our evaluation, we evaluate on the standard first 1000 images of the dataset, to be directly comparable to experiments run in other papers, e.g. \cite{prima,crown}, except for MLP $5\times 500$ which is not reported in \cite{prima,crown} and takes a large amount of time, for which we only test on the first 200 images. Each data example is associated with a $\varepsilon>0$ for the $L^\infty$ norm, and a target label for verification.

\subsection{Chosing nodes based on Compensation strength}

The first group of experiments we run, tests the accuracy of chosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly chosing the same number $K$ of nodes, to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.

@@

We now turn to evaluating chosing ReLU nodes in two consecutive layers, focusing on the uncertainty of nodes in the second layers, wrt ReLU nodes in the first and second layer.
The bounds for nodes of the second layers are computed exactly. 
Let $d$ be a neuron of the third layer.
We keep the previous evaluation for ranking nodes in the previous (second) layer. 
Once the set $Z$ of selected nodes has sufficiently many nodes $c,c'$ in the second layer, adding $b,b'$ to $Z$ allows to take into account accurately the pairs of paths of the form $(a b c d, a b' c' d)$ for all $\{c,c'\} \in Z$. We thus define 
$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min(weight(abcd),weight(ab'c'd))$ and the associated $comp(b)$, and select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.

>>>>

The local robustness verification is performed on DNNs trained for the MNIST image dataset as its the only standard DNNs (MLP $5\times 100$, $5\times 200$, $8 \times 100$, $8 \times 200$) benchmarked by \cite{crown} not using robust training, and they are the hardest DNNs to verify, despite their relatively limited size (600 to 1600 neurons in hidden layers). Indeed, today's efficient methods leave at least $14\%$ to $20\%$ of the images neither certified robust nor with an attack to robustness found, making them interesting DNNs to consider where to improve accuracy of efficient techniques. We also test on the larger MLP $6\times 500$, not previously tested in \cite{crown}. MNIST contains grayscale images of size $28 \times 28$ pixels ($752$ input neurons). For our evaluation, we evaluate on the standard first 1000 images of the dataset, to be directly comparable to experiments run in other papers, e.g. \cite{prima,crown}, except for MLP $5\times 500$ which is not reported in \cite{prima,crown} and takes a large amount of time, for which we only test on the first 200 images. Each DNN is associated with a $\varepsilon>0$ for the $L^\infty$ norm.
%, and a target label for verification.

\subsection{Choosing nodes based on Compensation strength}

The first group of experiments we run, tests the accuracy of choosing a set $Z$ of $K$ nodes using compensation strength, compared with randomly choosing the same number $K$ of nodes, to understand if the choice is meaningful or any set $Z$ with the same size will result in a similar accuracy.

@@

We now turn to evaluating choosing ReLU nodes in two consecutive layers, focusing on the uncertainty of nodes in the second layers, wrt ReLU nodes in the first and second layer.
The bounds for nodes of the second layers are computed exactly. 
Let $d$ be a neuron of the third layer.
We keep the previous evaluation for ranking nodes in the previous (second) layer. 
Once the set $Z$ of selected nodes has sufficiently many nodes $c,c'$ in the second layer, adding $b,b'$ to $Z$ allows to take into account accurately the pairs of paths of the form $(a b c d, a b' c' d)$ for all $\{c,c'\} \in Z$. We thus define 
$comp(b,b')=\sum_a \sum_{c,c' \in Z} \val_{\vx}(a) \min(weight(abcd),weight(ab'c'd))$ and the associated $comp(b)$, and select iteratively nodes $b$ (first layer) or $c$ (second layer) by selecting the heaviest $comp(b)$ or $comp(c)$.
